---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# baseballmexR

<!-- badges: start -->
<!-- badges: end -->

`baseballmexR` is a package written for R focused on mexican baseball analysis based on the `baseballr` and `sabRmetrics` packages. It includes functions for scraping [statsapi.mlb.com.com](https://www.statsapi.mlb.com/) focused on the Mexican Pro Baseball leagues LMB and LMP.

## Installation

You can install the development version of baseballmexR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("axelmora/baseballmexR")
```

## Example

The package consists mainly of data acquisition for the Mexican League (LMB) and the Winter Mexican League (LMP).

For example, if you want to see the teams for a specific league, you can use the `teams()` function. Just pass the league you want (lmb or lmp):

```{r teams}
library(baseballmexR)
teams(league = "lmb")
```

For see the schedule for a league in a specific year, you can use the `schedule()` function. Just pass the season and the league:

```{r schedule}
schedule(season = 2024, league = "lmp")
```

You can also pull data for a specific stat type and season for a league. Here are the results hitting stats for the 2023 season in the LMB:

```{r stats}
stats(league = "lmb", stat_group = "hitting", stat_type = "season", season = 2024, player_pool = "all")
```
